Flesh Simulation in the Field of Animation

### 2020-03-24 LaTeX-Master-Vorlage/chapter/Background.tex
working on bg, def. gradient

\subsection{Deformation}
If we apply a force over an object, the object itself undergoes a deformation. This behavior is intuitively clear. But how do we formalize this in a mathematical construct?

In the following, I will be consistent with most previous literature in continuum mechanics and use the term \textit{strain} as a measure of deformation and \textit{stress} as the force per unit area.

\todoredefined[inline]{
TODO: Decide whether to include the above paragraph and how to connect it better to the paper.
}

We can formalize the behaviour of a deformation. Graphically, one can imagine a deformation with the help of a two dimensional deformation map as shown in Fig. \ref{fig:deformationmap}. The ellipse on the left side represents an object or material in its rest state. A function $\phi$ maps this rest state of the ellipse to a deformed state as shown on the right side. Mathematically speaking, this means that we can map each point of a chosen object from its rest state to a deformed one.

@@

Each particle $X$ of a body can be characterized by a vector $\mathbf{x}$ containing its coordinates. If the particles undergo a displacement, we can describe their new coordinate vector with 
\[
	\check{\mathbf{x}} = \phi (\mathbf{x}).
\]

@@

\todoredefined[inline]{
TODO: Explain strain and stress and their meaning for later use in material constants (not explained in paper). Include own image instead of the one here?
}

\subsection{Deformation Gradient}
With the help of the deformation gradient \textbf{F}, we can calculate the change in volume and length of an object during a deformation.
For my needs, I am defining the deformation gradient analogous to the authors of \textit{\acrshort{snh}}:

>>>>

\subsection{Deformation}
If we apply a force over an object, the object itself undergoes a deformation. This behavior is intuitively clear. But how can we formalize it?

Graphically, we can imagine a deformation with the help of a two dimensional deformation map as shown in Fig. \ref{fig:deformationmap}. The ellipse on the left side represents an object or material in its rest state. A function $\phi$ maps this rest state of the ellipse to a deformed state as shown on the right side.

@@

This means that we can map each particle of a chosen object from its rest state (at time $t_0 = 0$) to a deformed one. Each particle $X$ of a body can be characterized by a vector $\mathbf{x}$ containing its coordinates. If the particles are displaced after a time $t$, we can describe their new coordinate vector with 
\[
	\check{\mathbf{x}} = \phi (\mathbf{x}, t).
\]
If we for example consider a \textit{Translation}, every particle is displaced by the same distance and direction. Thus we can calculate $\check{\mathbf{x}}$ with
\[
	\check{\mathbf{x}} = \mathbf{x} + \mathbf{c}(t)
\]
where $\mathbf{c}$ is a vector that only depends on $t$ (\cite{Spencer1980}, p.63).

\todoredefined[inline]{
TODO: Include own image instead of the one here? \\
Include this? \\
In the following, I will be consistent with most previous literature in continuum mechanics and use the term \textit{strain} as a measure of deformation and \textit{stress} as the force per unit area.
}

\subsection{Deformation Gradient}
The deformation gradient \textbf{F} can be obtained by deriving $\phi$. It is therefore the derivative of...

\begin{wrapfigure}{r}{5.5cm}
\centering
	\includegraphics[width=6.5cm]{resources/stretch_plot.png}
	\caption{Stretching of a rectangle}
	\label{stretch:1}
\end{wrapfigure}

We can take a simple deformation in 2D to illustrate \textbf{F}. We can stretch an area in the following way:
\[
	Here comes formulas
\]
This is illustrated in \ref{stretch:1}.

@@

With the help of the deformation gradient \textbf{F}, we can calculate the change in volume and length of an object during a deformation.
For my needs, I am defining the deformation gradient analogous to the authors of \textit{\acrshort{snh}}:
